\documentclass[12pt,a4paper]{responses}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\newcommand\degree{\ensuremath{{}^\circ}}
%%\pagestyle{empty}
%%\renewcommand\caption[1]{}
%%\linenumbers
\setlength{\parskip}{12pt}
\setlength{\parindent}{0pt}

\begin{document}
Dear Editor,

thank you for your constructive comments.  We have implemented your suggestions,
as detailed below.

\textit{1) We need a doi! As authors note, they desire a sequence of ESSD
  preliminary identifier first, for inclusion in the metadata of their product
  which will then carry its own doi, followed by submission of a revised
  manuscript including that reference doi-labelled data product. To facilitate
  this sequence, use this doi for the discussion paper:
  https://doi.org/10.5194/essd-2018-43. It should resolve correctly once you
  have submitted the revised manuscript.}

The dataset DOI is included in the revised submission, and the manuscript DOI is
included in the global attributes of each NetCDF file.  Mission accomplished!
Thank you and Anna for making these bidirectional references possible.

\textit{2) A small data source table could help: url for the specific version of the
CALIOP product used here, url for ceilometer data from Weather Underground (with
note of any geographic constraints or filtering), doi for the CBASE algorithm as
described and provided. Goal: to give a user easy access to all necessary
products rather than expecting them to search through text for url links.}

Good suggestion, which we have implemented.

\textit{3) Small issue but in the version as submitted, Figures and Tables section
starts before the Reference section ends. Pagination issue? }

Thank you for catching that.  Corrected.

Sincerely,

Johannes M\"ulmenst\"adt for the authors

\end{document}
